The benefits of an extended feature space in a machine learning bot for the game Schnapsen

### 2018-02-01 Text/paper.tex

\documentclass[a4paper,11pt]{article}

@@

\end{enumerate}
\end{document}

>>>>

<<<<<<< HEAD
\documentclass[a4paper,11pt]{article}

\begin{center}
\begin{tabular}{| r | r | r | r || r |}
\hline
      & \textbf{rand} & \textbf{bully} & \textbf{rdeep} & \textbf{Total} \\ \hline
      ml\_minimal & -2,65\% & -4,45\% & +35,4\% & \textbf{+1,45\%}   \\ \hline
      ml\_stripped & -15\% & -3,76\% & +10,11\% & \textbf{-6,85\%}  \\ \hline
      ml\_enriched & +1,73\% & -9,01\% & +10,5\% & \textbf{-1,85\%} \\ \hline
      ml\_advanced & -1,15\% & -7,76\% & +13,6\%& \textbf{-2,15\%}  \\ \hline
      ml\_combined & +9,58\% & -13,35\% & +6,61\% & \textbf{-0,85\%}  \\ \hline \hline
      Average improvement & \textbf{-1,5\%} & \textbf{-7,67\%} & \textbf{+15,24\%} &\textbf{-2,05\%} \\ \hline
\end{tabular} \\
\end{center}

Notable for the results of the tournaments against the bully bot are the following points. First of all, the stock ml bot performed the best of all bots. In figure 2 this is clearly noticable. Secondly,  ml\_stripped and ml\_minimal peformed comparable to ml bot. Therefore, we may conclude the smaller feature spaces do not cause a heavy impact on the performance of a learning bot. The last and most remarkable finding is the peformance of the ml\_enriched and ml\_combined bots. All bots with larger feature spaces peformed worse than ml bot. However, ml\_enriched and ml\_combined performed the worst with a performance decrease of approximately 9\%.

\clearpage
\section{Appendix}
\subsection{Overview of machine-learning bots' feature spaces}
\subsection{ml\_minimal}
\begin{itemize}
\item Perspective information
\item Player 1's point count
\item Player 2's point count
\end{itemize}
\subsection{ml\_stripped}
\begin{itemize}
\item Perspective information
\item Player 1's point count
\item Player 2's point count
\item The phase
\item The stock size
\item The leader
\item Whose turn it is currently
\item The played card of the opponent
\end{itemize}
\subsection{ml\_enriched}
\begin{itemize}
\item Perspective information
\item Player 1's point count
\item Player 1's point count squared
\item Player 1's point count cubed
\item Player 2's point count
\item Player 2's point count squared
\item Player 2's point count cubed
\item Player 1's pending points
\item Player 1's pending points squared
\item Player 1's pending points cubed
\item Player 2's pending points
\item Player 2's pending points squared
\item Player 2's pending points cubed
\item The trump suit
\item The phase
\item The stock size
\item The leader
\item Whose turn it is currently
\item The played card of the opponent
\end{itemize}
\subsection{ml\_advanced}
\begin{itemize}
\item Perspective information
\item Player 1's point count
\item Player 2's point count
\item Player 1's pending points
\item Player 2's pending points
\item Difference between player 1 and player 2's point count
\item Difference between player 1 and player 2's pending point count
\item The trump suit
\item Trump card ratio (Number of trump cards in hand / total number of cards in hand * 100)
\item High-ranking card ratio (Number of 10's and A's in hand / total number of cards in hand * 100)
\item The phase
\item Number of trump cards in hand in phase 2
\item The stock size
\item The leader
\item Whose turn it is currently
\item The played card of the opponent
\item Number of cards in same suit as opponent's played suit in hand.
\item Number of points in hand squared ($card1^2$ + $card2^2$ ...)
\end{itemize}

\item Game output

\item 
\end{enumerate}
\section{Worksheet III}
\begin{enumerate}
\item The added code:
\begin{lstlisting}[language=bash]
value = self.heuristic(next_state)

\end{enumerate}
=======
\documentclass[a4paper,11pt]{article}

@@

\end{enumerate}
>>>>>>> 84a742d35e719823e996e26633d936ee2353a31e
\end{document}
